% main.tex — JKCS (Journal of the Korean Ceramic Society) submission
% Springer Nature sn-jnl template
% NOTE: Switch to sn-jnl class when the correct version is available.
%       Current build uses article class for compatibility.
\documentclass[12pt,a4paper]{article}

%%% Packages %%%
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue]{hyperref}
\usepackage[margin=25mm]{geometry}

%%% SI units setup %%%
\sisetup{
  per-mode=symbol,
  inter-unit-product=\ensuremath{\cdot},
}

\begin{document}

\title{Bayesian Optimization of Gyroid TPMS Catalyst Support Geometry
  for Pressure Drop and Surface Area Using Lattice Boltzmann Method}

\author{Hyun-Kyu Tae\footnote{Corresponding author. E-mail: thk@example.com} \\
  \small Affiliation TBD, Republic of Korea}

\date{}
\maketitle

\begin{abstract}
Triply periodic minimal surface (TPMS) structures, particularly the gyroid,
have attracted attention as catalyst supports due to their high surface-area-to-volume
ratio and tunable porosity. In this study, we apply Bayesian optimization (BO)
to the design of gyroid catalyst supports, exploring the unit-cell size $a$
and threshold parameter $t$ to balance specific surface area $S_v$ against
pressure drop $\Delta P$. A D3Q19 multiple-relaxation-time lattice Boltzmann
method (MRT-LBM) solver implemented in Taichi is used to evaluate
Darcy permeability $K$ for each candidate geometry. One hundred BO evaluations
yield 50 Pareto-optimal designs, from which five representative configurations
(A--E) are selected for detailed characterization, including GHSV-dependent
pressure loss, Forchheimer nonlinear regression, flow mixing metrics,
and numerical reproducibility analysis.  Results show that designs with
$a = 3$--$\SI{6}{\milli\meter}$ achieve $S_v > \SI{2000}{\per\meter}$
while maintaining $\Delta P < \SI{50}{\pascal}$ at the reference GHSV,
offering practical trade-offs for ceramic catalyst support applications.
\end{abstract}

\noindent\textbf{Keywords:} Gyroid; TPMS; Lattice Boltzmann method;
Bayesian optimization; Catalyst support; Permeability

\input{sections/01_introduction}
\input{sections/02_methods}
\input{sections/03_results}
\input{sections/04_discussion}
\input{sections/05_conclusion}

\section*{Data Availability}
The simulation code, input parameters, and result datasets used in this study
are available at the project repository upon reasonable request.

\section*{Declarations}

\begin{itemize}
\item \textbf{Conflict of interest:} The authors declare no conflict of interest.
\item \textbf{Author contributions:} H.-K.\ Tae conceived the study, developed
  the LBM solver and BO pipeline, performed simulations, and wrote the manuscript.
\end{itemize}

\section*{Acknowledgements}
The authors thank the contributors of the Taichi programming framework
and the scikit-optimize library.

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
